\cvsection{Evaluation and Consulting Experience}

\subsection{Independent Consulting}
\begin{cvtable}
    \cvitem{2024 -- 2025}
        {\color{cvsectioncolor}{Entrepreneurial Mindset and Cultural Wealth in Engineering \\(EM-FYE)}}
        {\textbf{Northeastern University}}
        {Developed and led the data collection and analysis plan. Deployed and validated measurement tools. Mentored first-year education researchers from research planning through dissemination.}
\end{cvtable}

\subsection{Quality Evaluation Designs - Associate Consultant}
\begin{cvtable}
    \cvitem{2024 -- 2025}
        {\color{cvsectioncolor}{Advocacy Building Campaign for Engineering Education Research \\(ABC for EER)}}
        {\textbf{Clemson University}}
        {Developed and led the evaluation plan for the ABC for EER. Supervised a graduate student through data collection, analysis, and reporting. Created interim reports.}
    \cvitem{\textit{In Review}}
        {\color{cvsectioncolor}{Peer Review as an Inclusive Mentoring Experience \\(PRIME)}}
        {\textbf{Clemson University}}
        {Led evaluation plan and budget development for NSF BPE proposal submission.}
\end{cvtable}

\subsection{Quality Evaluation Designs - Assistant Consultant}
\begin{cvtable}
    \cvitem{2025}
        {\color{cvsectioncolor}{Penn State Acoustics Program \\(PSA Program)}}
        {\textbf{Penn State University}}
        {Led qualitative data collection and analysis, and conducted quantitative data analysis for evaluation of the PSA Program. Assisted in developing program recommendations and the final report.}
    \cvitem{2024 -- 2025}
        {\color{cvsectioncolor}{RIEF - Virtual Community of Practice \\(RIEF: VCoP)}}
        {\textbf{University of Georgia}}
        {Led qualitative data collection and analysis for evaluation of the VCoP initiative for the NSF RIEF program. Contributed to project update memo.}
    \cvitem{}
        {\color{cvsectioncolor}{IGE - Personalized Learning Module for Graduate STEM Education \\(IGE: PLM)}}
        {\textbf{University of Pittsburgh}}
        {Assisted with conducting interviews for qualitative components.}  
    \cvitem{2024}
        {\color{cvsectioncolor}{Engineering Education and Research Centers \\(EEC/ERC)} }
        {\textbf{NSF/ASEE}}
        {Led quantitative and qualitative analysis and supported data collection for evaluation of the NSF EEC annual grantees conference and ERC biennial meeting. Contributed to final report.}
    \cvitem{}
        {\color{cvsectioncolor}{Capacity Building for Research at Minority Serving Institutions (CyBR-MSI)}}
        {\textbf{NSF/ASEE}}
        {Led data collection and analysis for evaluation of the CyBR-MSI initiative. Developed recommendations for stakeholder groups within the program and contributed to final report.}
\end{cvtable}