%  Insert Research Experiences
\cvsection{Research Experience}

\subsection{Graduate Research Assistant}
\begin{cvtable}
    \cvitem{October, 2024 -- ongoing}
        {\color{cvsectioncolor}\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2429719&HistoricalAwards=false}{\underline{EMPOWERS}} - PI: Dr. Karen High}
        {\textbf{Clemson University, SC}}
        {Led the design and implementation of a university-wide research and evaluation plan for NSF-funded (IGE) study on the systemic impact of holistic mentor training. Managed three graduate and three undergraduate researchers. Contributed to institutional change efforts through data-driven evaluation strategies.}
    \cvitem{May, 2022 -- ongoing}
        {\color{cvsectioncolor}\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2144213&HistoricalAwards=false}{\underline{VECTORS}} - PI: Dr. Kristin Frady}
        {\textbf{Clemson University, SC}}
        {Led implementation of research methods for an NSF-funded (CAREER) study on strengths and experiences of vertical transfer students. Supported PI in data collection, analysis, and dissemination. Contributed to the development of a statewide transfer student dashboard for South Carolina}
    \cvitem{May, 2022 -- May, 2023}
        {\color{cvsectioncolor}\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2037807&HistoricalAwards=false}{\underline{PERT}} - PI: Dr. Lisa Benson}
        {\textbf{Clemson University, SC}}
        {Supported research and evaluation efforts for an NSF-funded (EAGER) study on mentored peer review training for journal and proposal reviews. Collaborated with evaluators and PIs to conduct and analyze qualitative data. Developed annual report and contributed to a subsequent NSF (BCSER) proposal.}
    %\cvitem{May, 2020 -- May, 2022}
        %{\color{cvsectioncolor}SVF - PI: Dr. Michael Childress}
        %{\textbf{Clemson University, SC}}
       % {Led research for a NOAA-funded study on the impact of theatrical arts in promoting public climate change awareness. Contributed to program facilitation and evaluation efforts.}
\end{cvtable}

\subsection{Professional Research Associate}
\begin{cvtable}
    \cvitem{Aug, 2017 -- May, 2020}
        {\color{cvsectioncolor}\href{https://brickandtile.org/}{\underline{National Brick Research Center} (NBRC)}}
        {\textbf{Clemson University, SC}}
        {Managed and trained five employees in materials engineering testing for ceramics. Led the development and implementation of internal and external curricula for industry professionals and university students. Conducted analytical testing, managed instrument calibration, and ensured compliance with industry standards. Received certifications in ASTM testing, ISO training, X-ray diffraction techniques, and X-ray fluorescence techniques.}
\end{cvtable}